---
title: "Seed Anti-Microbial Peptides prediction"
subtitle: "-- with deep learning methods"
author: "Shuang PENG"
institute: "IJPB, INRAE Versailles"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: ["default", "fc", "fc-fonts"]
    lib_dir: libs
    nature:
      beforeInit: "macros.js"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(knitr.duplicate.label = 'allow')
```

```{r xaringan-scribble, echo=FALSE}
xaringanExtra::use_scribble()
```

class: inverse, center, middle

# Content

.left[
- Anti-Microbial Peptides

- Machine-Learning Prediction Method

- The Problematic
]

---

```{r child='introduction.Rmd'}
```

---

class: inverse, center, middle

# Problematic: we don't have enough annotated data

.left[
- Data pre-traitement
  - deep learning "de bout en bout"
  
- Reusable model
  - Transfer learning
  
- Supervised learnring without annotation
  - self-supervised learning
]

---

```{r child='methodology.Rmd'}
```

---

class: inverse, center, middle

# Thanks !
