---
title: "Seed Anti-Microbial Peptides prediction"
subtitle: "-- with deep learning methods"
author: "Shuang PENG"
institute: "IJPB, INRAE Versailles"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: ["default", "fc", "fc-fonts"]
    lib_dir: libs
    nature:
      beforeInit: "macros.js"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(knitr.duplicate.label = 'allow')
```

```{r xaringan-scribble, echo=FALSE}
xaringanExtra::use_scribble()
```

class: inverse

# Content

<br><br>

## Anti-Microbial Peptides

<br><br>

## Machine-Learning Prediction Method

<br><br>

## The Problematic

---

```{r child='introduction.Rmd'}
```

---

class: inverse

# Problematic: we don't have enough annotated data

<br>

## Without Data pre-traitement ? 
### deep learning "de bout en bout"

--

## Reusable model ? 
### transfer learning
  
--
  
## Supervised learnring without annotation ? 
### self-supervised learning

---

```{r child='methodology.Rmd'}
```

---

class: inverse, center, middle

# Thanks !
